\section{Prevalence}

\subsection{Population-based surveys}
The best way to measure the prevalence of TB is through national population-based surveys of TB disease\cite{18713496}\cite{WHO2011}. Data from such surveys are available for an increasing number of countries (Chapter 2). It should be noted, however, that measurements of prevalence are typically confined to the adult population. Furthermore, prevalence surveys exclude extrapulmonary cases and do not allow the diagnosis of cases of culture-negative pulmonary TB. 

TB prevalence all forms and all ages ($P$) is measured as: bacteriologically-confirmed TB prevalence among those aged ≥15 measured from national survey ($p_{adult}$), adjusted for pulmonary TB in children ($p_{child}$) and extra-pulmonary TB all ages ($p_{ep}$):

$p_{pulm} = c p_{child} + (1 − c) p_{adult}$

$P = \frac{p_{pulm}}{1 - p_{ep}}$


\subsection{Indirect estimates}
When there is no direct measurement from a national survey of the prevalence of TB disease, prevalence is the most uncertain of the three TB indicators used to measure disease burden. This is because prevalence is the product of two uncertain quantities: (i) incidence and (ii) disease duration. The duration of disease is very difficult to quantify because it cannot be measured during surveys of the prevalence of TB disease (surveys truncate the natural history of disease). Duration can be assessed in self-presenting patients, but there is no practical way to measure the duration of disease in patients who are not notified to NTPs.

Indirect estimates of prevalence were calculated according to the following equation:

$P = \sum I_{i,j} d_{i,j}, i \in \lbrace 1, 2\rbrace, j \in \lbrace 1, 2\rbrace$

where the index variable $i$ denotes HIV+ and HIV–, the index variable $j$ denotes notified and non-notified cases, $d$ denotes the duration of disease in notified cases and $I$ is total incidence. In the absence of measurements, we did not allow duration in notified cases to vary among countries. Given their underlying uncertainty, prevalence estimates should be used with great caution in the absence of direct measurements from a prevalence survey. Unless measurements were available from national programmes (for example, Turkey), assumptions of the duration of disease were used as shown in Table 1.



  