\subsection{Disaggregation of TB mortality by age and sex}

\subsubsection{TB deaths among HIV-negative people}

From the age-specific adjusted (for coverage and ill-defined causes) number of deaths from VR, we first estimated the ratio $r_2$ of rates in children ($M_{0-14}$) compared to adults ($M_{15+}$) (\ref{eqn:r2}). The estimation of $r_2$ was based on a chained equations multiple imputation approach. The  imputation model covariates included total notifications, population proportion aged more than 65 years, an indicator variable for the epidemiological  region and whether a country was one of the 22 high-burden countries. The overall mortality rate for all ages ($M$) can be expressed as a weighted average of mortality in children and adults, where $c$ is the proportion of children among the general population (\ref{eqn:M}).


\begin{align}
r_2 &= \frac{M_{0-14}}{M_{15+}} \label{eqn:r2} \\
M &= c M_{0-14} + (1 - c) M_{15+} \label{eqn:M}
\end{align}


In countries with VR or mortality survey data, $M_{0-14}$ is directly measured. For countries without VR data, an imputation step is necessary where the ratio $r_2$ is predicted from a regression model with risk factors known to be associated with TB. The following variables were investigated for inclusion in the model: infant mortality rate per 1000 live births; gross domestic product per capita; HIV prevalence among the general population; the percentage of the total population aged <15 and ≥65 years; the TB treatment suc­cess rate; the total number of newly notified TB cases per year; whether or not a country had a high or low burden of MDR-TB; whether a country was among the 22 HBCs or not. For the sex disaggregation of TB mortality among adults ($M_{15+}$), we use sex-specific adjusted (for coverage and ill-defined causes) number of deaths from VR to estimate mortality rates in men $M_m$  and women $M_w$ (\ref{eqn:mm}). The ratio of these rates $r_3$ (\ref{eqn:r3}) is either directly measured in countries with VR data or imputed in countries without.


\begin{align}
M_{15+} &= M_w + M_m \label{eqn:mm} \\
r_3 &= \frac{M_m}{M_w} \label{eqn:r3}
\end{align}



\subsubsection{TB deaths among HIV-positive people}

TB deaths among HIV-positive people were disaggregated by age and sex using the assumption that the child to adult and men to women ratios are the same as the sex ratios of AIDS deaths estimated by UNAIDS, which are estimated for all countries in the world. Once ratios are calculated, equations (\ref{eqn:r2})-(\ref{eqn:r3}) can be used to complete disaggregation of TB deaths among HIV-positive people in children, men and women.
